sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-09 doc/paper.Rmd
Remove 2 pardiso refs

We ran a simple speed comparison between sdmTMB, inlabru, and mgcv for fitting a SPDE spatial random field model to 1000 data points with Gaussian error across a range of mesh resolutions (Fig. \@ref(fig:timing)).
In this test, for mesh resolutions under 500 nodes, sdmTMB fit the models the fastest.
inlabru was the least affected by mesh resolution and beyond 500 nodes was faster than sdmTMB with default sdmTMB settings.
mgcv was slightly slower than sdmTMB and was more affected by mesh resolution.
With the random effect normalizing constant calculated in R (`normalize = TRUE`), sdmTMB was the fastest across all mesh resolutions (this option may not be possible or as fast for all models).
Results with up to an order of magnitude more data points slightly shift the lines up without affecting the overall pattern substantially (not shown).
Our test was with one core and default R algebra libraries; all packages could run faster with optimized libraries and parallel processing.
Results with optimized math libraries (openBLAS: @penblas2021 and PARDISO: @pardiso-7.2a, @pardiso-7.2b, @pardiso-7.2c) resulted in a ~10% speed increase for sdmTMB and inlabru and a ~7--9-fold speedup for mgcv.
<!-- Note two other references for PARDISO were listed as required here https://pardiso-project.org/manual/manual.pdf -->

>>>>

We ran a simple speed comparison between sdmTMB, inlabru, and mgcv for fitting a SPDE spatial random field model to 1000 data points with Gaussian error across a range of mesh resolutions (Fig. \@ref(fig:timing)).
In this test, for mesh resolutions under 500 nodes, sdmTMB fit the models the fastest.
inlabru was the least affected by mesh resolution and beyond 500 nodes was faster than sdmTMB with default sdmTMB settings.
mgcv was slightly slower than sdmTMB and was more affected by mesh resolution.
With the random effect normalizing constant calculated in R (`normalize = TRUE`), sdmTMB was the fastest across all mesh resolutions (this option may not be possible or as fast for all models).
Results with up to an order of magnitude more data points slightly shift the lines up without affecting the overall pattern substantially (not shown).
Our test was with one core and default R algebra libraries; all packages could run faster with optimized libraries and parallel processing.
Results with optimized math libraries (openBLAS: @penblas2021 and PARDISO: @pardiso-7.2c) resulted in a ~10% speed increase for sdmTMB and inlabru and a ~7--9-fold speedup for mgcv.
<!-- Note two other references for PARDISO were listed as required here https://pardiso-project.org/manual/manual.pdf -->
